---
title: "Homework 6 solutions"
author: "Zaynub Ibrahim"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(p8105.datasets)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

First we import and clean data. 

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex), 
    frace = as.factor(frace), 
    malform = as.factor(malform),
    mrace = as.factor(mrace),
    smoken = as.factor(smoken), 
    frace = recode(frace,"1" = "white", "2" = "black", "3" = "asian", "4" = "puerto rican", "8" = "other" ),  fincome = fincome * 100)
```

For cleaning the data, I changed variables to factors and re-coded the race variable to reflect the name of the actual race. I also multiplied the income variable by 100 to reflect the actual value of income for simplicities sake. There are `r sum(is.na(baby_df))` missing values in the entire dataframe. 


Now I will fit a full saturated model of the data. 
```{r}
full_model = lm(bwt~., data = baby_df)
summary(full_model)
```

Next I will fit a hypothesized model for significant underlying factors of birthweight.  
```{r}
hyp_model = lm(bwt ~ babysex + bhead + blength + fincome + gaweeks + mrace + malform + ppbmi, data = baby_df)

hyp_model %>% 
  broom::glance()

hyp_model %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

Next I will add residuals. 
```{r}
plot_df = baby_df %>% 
  add_residuals(hyp_model) %>%
  add_predictions(hyp_model) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(aes(alpha = 0.30))

print(plot_df)
```

Next I will compare this model to two others. The first is using length at birth and gestational age as predictors (main effects only).

```{r}
model_one = lm(bwt ~ blength + gaweeks, data = baby_df)
summary(model_one)
```

The second is using head circumference, length, sex, and all interactions (including the three-way interaction) between these. 

```{r}
model_two = lm(bwt ~ bhead + babysex + blength + bhead*blength + bhead*babysex + babysex*blength + babysex*blength*bhead, data = baby_df)
summary(model_two)
```

Next I will use cross validation to to make a comparison of all the models. 
```{r}
crossval_df = crossv_mc(baby_df, 100)

crossval_df = 
  crossval_df %>% 
  mutate(train = map(train, as_tibble, 
         test = map(as_tibble)))

crossval_df =
  crossval_df %>% 
  mutate(fit1 = map(train, ~lm(bwt ~ babysex + bhead + blength + fincome + gaweeks + mrace + malform + ppbmi, data = .x)), 
         fit2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)), 
         fit3 = map(train, ~lm(bwt ~ bhead + babysex + blength + bhead*blength + bhead*babysex + babysex*blength + babysex*blength*bhead, .x))) %>%
  mutate(fit = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)), 
         fit1 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)), 
         fit2 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y)))

modelnames = c("Hypothesized Model", "Comparison Model 1", "Comparison Model 2")
```

Next I will plot the prediction error distribution. 


